---
title: "Map of Seven Wonders of Ancient World"
author: "Saurabh Arora"
date: "12/17/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE}

library("leaflet")
```
## Introduction
This document plots the seven wonders of the ancient world on a map.The seven wonders are:-

* Great Pyramid of Giza
* Hanging Gardens of Babylon
* Colossus of Rhodes (Exact location is not known, point to town of Rhodes)
* Lighthouse of Alexandria
* Temple of Artemis
* Statue of Zeus at Olympia
* Mausoleum at Halicarnassus

```{r echo=FALSE}
wondersdata <-data.frame(
  lat = c(29.979175,32.5355,36.166667,31.213889,37.949722,37.637861,37.0379),
  lng = c(31.134358,44.4275,28,29.885556,27.363889,21.63,27.424),
  image = c(
   "https://upload.wikimedia.org/wikipedia/commons/thumb/e/e3/Kheops-Pyramid.jpg/300px-Kheops-Pyramid.jpg",
   "https://upload.wikimedia.org/wikipedia/commons/a/ae/Hanging_Gardens_of_Babylon.jpg",
   "https://upload.wikimedia.org/wikipedia/commons/5/5f/Colosse_de_Rhodes_%28Barclay%29.jpg",
   "https://upload.wikimedia.org/wikipedia/commons/2/22/Lighthouse_-_Thiersch.png",
   "https://upload.wikimedia.org/wikipedia/commons/1/1d/Miniaturk_009.jpg",
   "https://upload.wikimedia.org/wikipedia/commons/c/c6/Statue_of_Zeus.jpg",
   "https://upload.wikimedia.org/wikipedia/commons/f/f4/The_ruins_of_the_Mausoleum_at_Halicarnassus.jpg"
  ),
  popup=c(
    "Great Pyramid of Giza",
    "Hanging Gardens of Babylon",
    "Colossus of Rhodes",
    "Lighthouse of Alexandria",
    "Temple of Artemis",
    "Statue of Zeus at Olympia",
    "Mausoleum at Halicarnassus"
  )
  )

```

```{r echo=FALSE}

map <- 
  leaflet() %>%
  addTiles()
for(i in seq(1:7)){
  c <- makeIcon(
  iconUrl = wondersdata["image"][i,],
  iconWidth = 1*31*215/230, iconHeight = 1*31,
  iconAnchorX = 1*31*215/230/2, iconAnchorY = 1*16
)
  map <- map %>% addMarkers(lat=wondersdata["lat"][i,],lng=wondersdata["lng"][i,],
                            icon=c,
                            popup=wondersdata["popup"][i,]
                          )
}
map
```

## Attribution

All content and images in this page are derived from wikipedia https://en.wikipedia.org/wiki/Wonders_of_the_World 